Weakly informative observations: not the winner

### 2020-02-07 inst/notthewinner.Rmd
more rewriting

(see how $H_1$ implies that someone is worse than me).  Observe that
$H_1$ and $H_2$ correspond to a restriction on allowable parameter
space.  The first step is to define a suitable likelihood function for
our data.

What we will do is combine ${\mathcal O}$ with other, perhaps more
informative, observations which we will take to be (conditionally)
independent of one another.  Firstly we will consider some highly
informative order statistics:

```{r}
(H <- hyper2(pnames=paste("p",1:5,sep="")) +
    order_likelihood(c(5,2,1,4)) + 
    order_likelihood(c(2,4,1)) + 
    order_likelihood(c(4,3,1)) + 
    order_likelihood(c(3,5)))
(mH0 <- maxp(H))
loglik(indep(mH0),H)
```

@@

(the numerical value of `small` is immaterial).

@@

We can present a support function for $H_0,H_1,H_2$:

@@

Now we make another observation ${\mathcal O}$ that is weakly
informative: that person `1` did not win:

@@

So `SLa` is a compound object that gives a likelihood function for the
joint observation of the order statistics and ${\mathcal O}$.  We can
find the MLE for different observations:

@@

To compare:

>>>>

(see how $H_1$ implies that someone is worse than me).  Observe that
$H_1$ and $H_2$ correspond to a restriction on allowable parameter
space.

To understand the informativeness of ${\mathcal O}$, we will consider
it in conjunction with some highly informative observations ${\mathcal
I}$ which are order statistics:

```{r}
(H <- hyper2(pnames=paste("p",1:5,sep="")) +
    order_likelihood(c(5,2,1,4)) + 
    order_likelihood(c(2,4,1)) + 
    order_likelihood(c(4,3,1)) + 
    order_likelihood(c(3,5)))
	```

We will firstly consider these observations in isolation, then later
combine them with ${\mathcal O}$ which we will take to be
(conditionally) independent.  The first step is to define a suitable
likelihood function for ${\mathcal I}$:q

```{r}	
(mH0 <- maxp(H))
loglik(indep(mH0),H)
```

@@

See how the constraint of $H_1$ is active, for at the evaluate
$p_1=p_4$ (the numerical value of `small` is immaterial).

@@

We can present a support function for $H_0,H_1,H_2$ for ${\mathcal
I}$:

@@

Now we make another observation ${\mathcal O}$ that is weakly
informative: person `1` did not win.  Package idiom is similar to the
perfectly uninformative observation considered above, except that we
remove every order that has person 1 winning:

@@

So `SLa` is a compound object that gives a support function for the
joint observation ${\mathcal I}$ and ${\mathcal O}$.  We can find the
MLE:

@@

We can now compare the support function for ${\mathcal I}$ with the
support function for ${\mathcal I}$ and ${\mathcal H}$:
